PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2022-08-16 main.tex
Replace y values in figure 8 with b_tilde

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/surfden_iso.png}
    \caption{Masses of the remaining bodies from the simulations
      listed in table \ref{tab:sim_properties}, in units of the
      isolation mass for $\tilde{b} = 2 \sqrt{3}$. Despite the vastly different initial solid surface density profiles, the orbital period inside of which the embryo masses exceed the isolation mass is very consistent.\label{fig:surfden_iso}}
\end{center}
\end{figure}

@@

In figure \ref{fig:surfden_iso}, we compare the masses of the resulting protoplanets and planetesimals in all four simulations to each other. Here, the masses are scaled by the isolation mass at the given orbital distance (see equation \ref{eq:iso}). In all four cases, the masses follow a similar trend: interior to about 60 days in orbital period, protoplanets grow to a factor of a few larger than $M_{iso}$. Exterior to this point, the protoplanet masses roughly stay near the isolation mass. Despite the drastically different solid surface density profiles used, the masses of the largest bodies in all four cases follow a similar trend with orbital period. This indicates that the highly efficient accretion mode seen at shorter orbital periods is dependent on the sizes of the individual bodies themselves, rather than how they are distributed. The transition visible near 60 days in all cases also supports our conclusion that planetesimal accretion is largely complete everywhere in the disk.

>>>>

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/surfden_b.png}
    \caption{Feeding zone width (see equation \ref{eq:iso} required to produce the final masses for the protoplanets from the simulations listed in table \ref{tab:sim_properties}. The horizontal dashed line indicates $\tilde{b} = 2 \sqrt{3}$. Despite the vastly different initial solid surface density profiles, the feeding zone width reaches the circular orbit value around $\sim$ 60 days. \label{fig:surfden_b}}
\end{center}
\end{figure}

@@

In figure \ref{fig: surfden_b}, we plot the masses of the resulting protoplanets and planetesimals in all four simulations in units of $\tilde{b}$ (see equation \ref{eq:iso}). Here, we assume that each embryo has reached its isolation mass, and that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the size of its feeding zone, which is set by the dynamics relevant at that location in the disk. By plotting the derived value of $\tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more clearly visible. As mentioned previously, $\tilde{b} = 2 \sqrt{3}$ (indicated by the horizontal dashed line) carries a special significance, being the minimum feeding zone width that a body can have. In all four simulations, the feeding zone width exceeds the minimum value in the inner disk and approaches $2 \sqrt{3}$ beyond $\sim$ 60 days. The orbital periods at which this transition occurs are remarkably similar, despite the vastly different solid surface density profiles used. This similarity indicates that the boundary between accretion modes is not dependent upon the surface density profile chosen, and also supports our conclusion that planetesimal accretion is largely complete everywhere in the disk.

%In figure \ref{fig:surfden_iso}, we compare the masses of the resulting protoplanets and planetesimals in all four simulations to each other. Here, the masses are scaled by the isolation mass at the given orbital distance (see equation \ref{eq:iso}). In all four cases, the masses follow a similar trend: interior to about 60 days in orbital period, protoplanets grow to a factor of a few larger than $M_{iso}$. Exterior to this point, the protoplanet masses roughly stay near the isolation mass. Despite the drastically different solid surface density profiles used, the masses of the largest bodies in all four cases follow a similar trend with orbital period. This indicates that the highly efficient accretion mode seen at shorter orbital periods is dependent on the sizes of the individual bodies themselves, rather than how they are distributed. The transition visible near 60 days in all cases also supports our conclusion that planetesimal accretion is largely complete everywhere in the disk.
